\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-15 paper.qmd
Added axis circle

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5)

@@

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5)

@@

```{r}
#| label: fig-scurve-true-sc
#| fig-cap: "Three views of the true model (grey points and lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (purple points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)."

>>>>

axis_scale <- 0.15 * limits
axis_pos <- -0.6 * limits
adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

scurve_proj1_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70")

@@

axis_scale <- 0.1 * limits
axis_pos <- -0.4 * limits
adj <- function(x) axis_pos + x * axis_scale
theta <- seq(0, 2 * pi, length = 50)
circle <- data.frame(c1 = adj(cos(theta)), c2 = adj(sin(theta)))

scurve_proj2_true_model <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
      geom_point(
        size = 0.8,
        alpha = 0.8,
        color = "#000000") +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#969696") + 
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes, 
    aes(x=x2, y=y2, label=rownames(axes)), 
    colour="grey50",
    size = 2.5) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70")

@@

```{r}
#| label: fig-scurve-true-sc
#| fig-cap: "Two views of the true model (grey lines) in $2\\text{-}D$ projections from $7\\text{-}D$, for the S-curve data (black points). The data is spread along the S shape, and does not vary much from this curve. (The **langevitour** software is used to view the data with a tour, and the full video is available at <https://youtu.be/I5GL23vLiw0>)."

### 2024-08-15 paper.tex
Added axis circle

\caption{\label{fig-scurve-true-sc}Three views of the true model (grey
points and lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for
the S-curve data (purple points). The data is spread along the S shape,
and does not vary much from this curve. (The \textbf{langevitour}
software is used to view the data with a tour, and the full video is
available at \url{https://youtu.be/I5GL23vLiw0}).}

>>>>

\caption{\label{fig-scurve-true-sc}Two views of the true model (grey
lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
S-curve data (black points). The data is spread along the S shape, and
does not vary much from this curve. (The \textbf{langevitour} software
is used to view the data with a tour, and the full video is available at
\url{https://youtu.be/I5GL23vLiw0}).}
